### 2018-04-18 experiments.tex
fix backslash

Figure \ref{hashbug} shows TSTL code for generating inputs to the {\tt
  datarray} algorithms.  The {\tt flatten_and_sort} function is needed because we care about actual differences in probability values, not simply the order of list, tuple, or dictionary items.  Running this harness using TSTL's {\tt
  --checkProcessDeterminism} flag required less than 10 seconds on
average to produce a test exhibiting process-level nondeterminism in
the {\tt calc\_marginals\_sumproduct} function (the only broken
algorithm).  Reducing this 60 step test to a minimal test of only 6 steps,
showing an extremely simple input producing the issue, 
required another 92 seconds.

>>>>

Figure \ref{hashbug} shows TSTL code for generating inputs to the {\tt
  datarray} algorithms.  The {\tt flatten\_and\_sort} function is needed because we care about actual differences in probability values, not simply the order of list, tuple, or dictionary items.  Running this harness using TSTL's {\tt
  --checkProcessDeterminism} flag required less than 10 seconds on
average to produce a test exhibiting process-level nondeterminism in
the {\tt calc\_marginals\_sumproduct} function (the only broken
algorithm).  Reducing this 60 step test to a minimal test of only 6 steps,
showing an extremely simple input producing the issue, 
required another 92 seconds.
